---
title: "10_import"
output: html_notebook
---

# Metro Interstate Traffic Volume Data


I will need the following libraries:

```{r libraries}
library(readxl)
library(assertr)
library(dplyr)
library(purrr)
library(janitor)
library(lubridate)
library(tidyr)
```


Now, I will load the data and examine it. I will also ensure that the names are in a clean format for use.

```{r load data}
Metro_Traffic <- read_excel("Metro_Interstate_Traffic_Volume.xlsx") %>%
  clean_names()

head(Metro_Traffic)

Metro_Traffic %>%
  map(class)

```

Before I delve too deeply in the data, I want to make sure there is no abnormal data in the dataset. To do so, I will use the assertr library to check different variables. 

First, let's make sure that the variable measuring cloud cover (in percent) lies between 0 and 100. 

```{r check cloud coverage}
Metro_Traffic %>%
  assert(within_bounds(0, 100), clouds_all)
```

Looks good! 


I also want to make sure that all traffic volume values are positive.

```{r}
Metro_Traffic %>%
  assert(within_bounds(0, 10000), traffic_volume)
```
Also looks good! 


Normally, I would also want to change the date and time to the correct format but, in this case, they already are. The data ranges from 2012 to 2018.

```{r check date and time}
str(Metro_Traffic$date_time)
min(Metro_Traffic$date_time)
max(Metro_Traffic$date_time)
```

