---
title: "40_modeling"
output: html_notebook
---

# Modeling the data

I will now add all of the new features to the data frame in order to prepare for modeling.
```{r add features to data}
Metro_Traffic_eng <- Metro_Traffic %>%
  rush_hour2("date_time") %>%
  fahrenheit("temp") %>%
  select(traffic_volume, everything()) %>%
  assert(in_set("TRUE", "FALSE"), am_rush_hour) %>%
  assert(within_bounds(-45, 110), temp_f)
```




The temperature variable has a few values at -459 degrees. This is obviously incorrect. I will remove these values since they lie so far from the acceptable range and replace them with NA. This is done with the mutate statement added in below. 

```{r fix std_rain}
Metro_Traffic_eng <- Metro_Traffic %>%
  rush_hour2("date_time") %>%
  fahrenheit("temp") %>%
  select(traffic_volume, everything()) %>%
  assert(in_set("TRUE", "FALSE"), am_rush_hour) %>%
  mutate(temp_f = replace(temp_f, temp_f<= -45, NA)) %>%
  assert(within_bounds(-45, 110), temp_f)
```


Now the data is ready for further modeling.

```{r}
Metro_Traffic_eng
```

